Determinants of Financial Well-Being: The Role of Demographics, Psychosocial Factors, and Financial Literacy

### 2024-12-03 paper/paper.qmd
Update scripts to follow the paper

corrplot(cor(continuous_vars), 
         method="color", 
         type="upper", 
         addCoef.col = "black",
         tl.col="black", 
         tl.srt=45)

```

@@

@@

par(mfrow=c(2,2))
plot(lm_model, which=1:4)
```

>>>>

corrplot(cor(continuous_vars),
  method = "color",
  type = "upper",
  addCoef.col = "black",
  tl.col = "black",
  tl.srt = 45
)
```

@@

```{r}
for (var in variables) {
  print(var)
  print(levels(data_cleaned[[var]]))
}
```

@@

par(mfrow = c(2, 2))
plot(lm_model, which = 1:4)
```
